Hypertension and microbiome

### 2019-02-05 articletwo.Rmd
Minor
Figure 4

if (exists(args)) {
    if ("time" %in% names(args) now <- args$time,

@@

maaslinplot <- plot_maaslin_heatmap_final(maas.results.df.signf %>% dplyr::filter(Variable != "HYPERTENSION"),
                      xlab.text="Genera",
                      beta.maxabs=max(abs(maas.results.df.signf[,'beta'])),
                      order.by.category=FALSE)

@@

@@

```{r Write figure 4}
fig4head <- "Bacteria causing dysentery and diarrhea contribute to third principal component"
fig4foot <- sprintf("Top 20 bacterial contributors to third principal coordinate at species level. Centered log ratio transform is performed for the compositional data. Third principal component explain %.1f%% of the total variation. Plasmid DNA is denoted using star.", pca.percentage[3])
writeimage(doc, 4, "cache/pca.pc3.png", fig4head, fig4foot)
```

>>>>

if (exists("args")) {
    if ("time" %in% names(args)) now <- args$time

@@

maaslinplot <- plot_maaslin_heatmap_final(maas.results.df.signf %>% dplyr::filter(Variable != "HYPERTENSION"),
                      beta.maxabs=max(abs(maas.results.df.signf[,'beta'])),
                      order.by.category=FALSE)

@@

```{r PC plot}
pca.prcomp.df <- pca.prcomp$x[,1:5] %>% data.frame
#pca.prcomp$sdev[1:20]^2/sum(pca.prcomp$sdev^2)
#cumsum(pca.prcomp$sdev[1:20]^2/sum(pca.prcomp$sdev^2))

X <- base::merge(meta(pseq.species), pca.prcomp.df, by=0, all=TRUE) %>%
    dplyr::rename(Sample_ID = Row.names)

X.res <- lapply(vectortolist(paste0("PC", seq(5))), function(axis) {
    modelstring <- paste0("%s ~  BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09 + ", axis)
    calculateglm(X, modelstring = modelstring, filterstr = "PC")
})

Z.df <-  do.call(rbind.data.frame, X.res) %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(p.value, method="BH"),
                  beta = estimate,
                  Feature = term)

p2 <- plot_maaslin_heatmap_final(Z.df , fname="Feature", pname="Name",
                                  xlab.text = "PC", signif="Qval", cluster=FALSE,
                                  v.title.name = "Effect size (PC)",
                                  ystr="reorder(Name, Qval)", sign.name="Significance.PC",
                                  no.sign.legend=TRUE)

ggsave(file = "cache/pca.p2.png", plot = p2, height = 8, width = 8, dpi = 300)

```

## Figure 5

@@

```{r Write figure 5}
fig4head <- "Bacteria causing dysentery and diarrhea contribute to third principal component"
fig4foot <- sprintf("Top 20 bacterial contributors to third principal coordinate at species level. Centered log ratio transform is performed for the compositional data. Third principal component explain %.1f%% of the total variation. Plasmid DNA is denoted using star.", pca.percentage[3])
writeimage(doc, 5, "cache/pca.pc3.png", fig4head, fig4foot)
```
